Ms 1

### 2017-09-28 ms1/ms1_display.Rmd
ms1: rearrange approp

@@

@@

@@

@@

```{r approp_graph}
pde_approp_table = read_tsv('tables/pde_approp_table.tsv') %>%
  #filter(year %in% c(2011, 2014)) %>%
  (function(df) bind_rows(
    df,
    df %>% group_by(year, tier, refill) %>%
      summarize(n=sum(n)) %>%
      mutate(antibiotic='overall')
  )) %>%
  filter(antibiotic %in% c(top_abx, 'overall')) %>%
  group_by(year, antibiotic) %>%
  mutate(f=n/sum(n)) %>%
  ungroup()

pde_approp_table %>%
  filter(year %in% c(2011, 2014)) %>%
  ggplot(aes(x=factor(year), y=f, fill=factor(tier))) +
  geom_bar(stat='identity') +
  facet_grid(~antibiotic) +
  theme_classic()
```

@@

```{r pre_approp_table}
pde_approp_trends = read_tsv('tables/pde_approp_trends.tsv') %>%
  filter(term=='year') %>%
  mutate(or=exp(3*estimate), adj.p=p.adjust(p.value, method='BH')) %>%
  select(antibiotic, or, adj.p)

pde_approp_table %>%
  filter(tier <= 2) %>%
  select(antibiotic, year, f) %>%
  group_by(antibiotic, year) %>%
  summarize(f=sum(f)) %>%
  ungroup() %>%
  spread(year, f) %>%
  left_join(pde_approp_trends, by='antibiotic') %>%
  mutate(raw_pct_change=(`2014`-`2011`)/`2011`,
         adj_pct_change=risk_ratio_f(or, `2011`) - 1) %>%
  mutate_at(vars(`2011`, `2014`, raw_pct_change, adj_pct_change),
            function(x) round(x*100, 2)) %>%
  select(antibiotic, `2011`, `2014`, raw_pct_change, adj_pct_change, adj.p) %>%
  arrange(raw_pct_change) %>%
  kable
```

>>>>

```{r approp_changes}
# read in the raw and trend data
pde_approp_table = read_tsv('tables/pde_approp_table.tsv') %>%
  (function(df) bind_rows(
    df,
    df %>% group_by(year, tier) %>%
      summarize(n=sum(n)) %>%
      mutate(antibiotic='overall')
  )) %>%
  filter(antibiotic %in% c(top_abx, 'overall')) %>%
  group_by(year, antibiotic) %>%
  mutate(f=n/sum(n)) %>%
  ungroup()

pde_approp_risk_2011 = pde_approp_table %>%
  # add up tiers 1 and 2
  filter(year==2011, tier <= 2) %>%
  group_by(antibiotic) %>%
  summarize(risk_2011=sum(f))

# compute risk ratios
pde_approp_trends = read_tsv('tables/pde_approp_trends.tsv') %>%
  filter(term=='year') %>%
  mutate(estimate=exp(3*estimate), # odds ratio over the whole time period
         std.error=sqrt(3)*std.error,
         adj.p=p.adjust(p.value, method='BH'),
         ci=1.96*std.error,
         ci_low=estimate-ci,
         ci_high=estimate+ci) %>%
  left_join(pde_approp_risk_2011, by='antibiotic') %>%
  # convert OR to RR (i.e., adjusted change)
  mutate_at(vars(estimate, ci_low, ci_high), function(x) risk_ratio_f(x, .$risk_2011 - 1)) %>%
  # convert to percents, and reverse direction (to make it *inapprop*)
  mutate_at(vars(estimate, ci_low, ci_high), function(x) -(x - 1)*100) %>%
  select(antibiotic, pct_change=estimate, ci_low, ci_high, adj.p) # now estimate is adjusted change
```

@@

ggplot(adjusted_changes, aes(x=antibiotic, y=pct_change, ymin=ci_low, ymax=ci_high)) +
  geom_hline(yintercept=0) +
  geom_bar(dat=adjusted_changes, stat='identity', fill=NA, color='black') +
  geom_errorbar(dat=adjusted_changes, width=0.5) +
  geom_point(dat=unadjusted_changes, aes(ymin=NULL, ymax=NULL), shape=1) +
  geom_point(dat=pde_approp_trends, color='blue', shape=1) +
  geom_errorbar(dat=pde_approp_trends, width=0.25, color='blue') +
  coord_flip() +
  xlab('') +
  ylab('adjusted change from 2011 to 2014 (%)') +
  scale_y_continuous(limits=c(-22, 32), breaks=c(-20, -10, 0, 10, 20, 30)) +
  theme_classic() +
  theme(axis.title.x = element_text(size=16),
        axis.text = element_text(size=16))

@@

The bars show the adjusted change in consumption. Black circles show unadjusted change in consumption. Blue shows the adjusted change in inappropriate prescribing.

### Adjusted changes in usage

@@

### Adjusted changes in inappropriate prescribing

```{r pde_approp_trends_table}
pde_approp_trends %>% kable
```

@@

```{r approp_graph}
pde_approp_table %>%
  #filter(year %in% c(2011, 2014)) %>%
  ggplot(aes(x=factor(year), y=f, fill=factor(tier))) +
  geom_bar(stat='identity') +
  facet_grid(~antibiotic) +
  theme_classic()
```

@@

```{r pre_approp_table}
